---
title: 'Reproducible Research: Peer Assessment 1'
output:
  pdf_document: default
  html_document:
    keep_md: yes
---


## Loading and preprocessing the data

*The data available in the git repository, so not downloaded again.*

Unzip the data and read the csv file to a variable.
```{r echo=TRUE}
unzip("activity.zip")

d <- read.csv("activity.csv")
```

## Histogram of Total steps per day
```{r echo=TRUE}
stepsPerDay <- aggregate(d$steps, by = list(d$date), FUN=sum)

hist(stepsPerDay$x, col="lightblue", breaks = 30, main="Steps per Day", xlab = "Steps", ylab = "Frequency")
```

## What is mean total number of steps taken per day?

### Mean
```{r echo=TRUE}
mean(stepsPerDay$x, na.rm = TRUE)
```

### Median
```{r echo=TRUE}
median(stepsPerDay$x, na.rm = TRUE)
```

## What is the average daily activity pattern?

Subset the steps based on interval
```{r echo=TRUE}
stepsByInterval <- aggregate(steps ~ interval, data = d, FUN = mean, na.action = na.omit)
```

Time series plot of avg steps per day
```{r echo=TRUE}
plot(x=stepsByInterval$interval, y=stepsByInterval$steps, type = 'l', xlab = "Interval(5 min)", ylab = "Steps", col="blue", main="Average Steps per Interval")
```

5 min interval having maximum steps on average
```{r echo=TRUE}
stepsByInterval[which.max(stepsByInterval$steps),1]
```


## Imputing missing values

1. Total no of missing values in steps column of the dataset
```{r echo=TRUE}
sum(is.na(d$steps))
```



## Are there differences in activity patterns between weekdays and weekends?
